Carrier phase and amplitude estimation for phase shift keying using pilots and data (Appendix)

### 2012-08-17 paper2.tex
Added to paper parts.

%opening
\title{Carrier phase and amplitude estimation for phase shift keying using pilots and data (Appendix)}
\author{Robby McKilliam, Andre Pollok, Bill Cowley 
\thanks{
Supported under the Australian Government’s Australian Space Research Program.
Robby McKilliam, Andre Pollok and Bill Cowley are with the Institute for Telecommunications Research, The University of South Australia, SA, 5095.
}}

@@

%set this to the number of the last equation in the previous document.
\setcounter{equation}{20}
\newcounter{lasteqplusone}
\setcounter{lasteqplusone}{\value{equation}}
\addtocounter{lasteqplusone}{1}

@@

Here we compile lemmas required for the proof almost sure convergence (Theorem~\ref{thm:consistency}) and asymptotic normality (Theorem~\ref{thm:normality}) from the paper~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  This document is not self contained and it is intended that the reader start at~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  The equation reference numbers in this document start at (\arabic{lasteqplusone}).  All equation numbers less than (\arabic{lasteqplusone}) refer back to~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  This document is separated into 3 sections.  Section~\ref{sec:proof-almost-sureappendix} contains those lemmas required for the proof of almost sure convergence (Theorem~\ref{thm:consistency}).  Section~\ref{sec:proof-asympt-normappendix} contains those lemmas required for the proof of asymptotic normality (Theorem~\ref{thm:normality}).  Section~\ref{sec:an-empirical-process} contains proofs for lemmas that arise during Section~\ref{sec:proof-asympt-normappendix}.  These involve the proof of~\emph{tightness} for certain empirical processes~\cite{Billingsley1999_convergence_of_probability_measures,Dudley_unif_central_lim_th_1999,Shorak_emp_proc_stat_2009}.

@@

It remains to show that $G_L^\prime(\hat{\lambda}_L) = 0$.  If $\sabs{G_L(\hat{\lambda}_L)} > 0$ then $\sabs{G_L(\lambda)}$ is differentiable at $\hat{\lambda}_L$ and, since $\hat{\lambda}_L$ is a maximiser of $\sabs{G_L(\lambda)}$,
\[
0 = \frac{d \sabs{G_L(\lambda)}}{d \lambda}(\hat{\lambda}_L) = \begin{cases} 
G_L^\prime(\hat{\lambda}_L), & G_L(\hat{\lambda}_L) > 0\\
-G_L^\prime(\hat{\lambda}_L), & G_L(\hat{\lambda}_L) < 0.
\end{cases}
\]
Thus, $G_L^\prime(\hat{\lambda}_L) = 0$ if $\sabs{G_L(\hat{\lambda}_L)} > 0$.  On the other hand $\sabs{G_L(\hat{\lambda}_L)} = 0$ only if $G_L(\lambda) = 0$ for all $\lambda \in \reals$, inwhich case $G_L^\prime(\hat{\lambda}_L) = 0$. 
\end{IEEEproof}

@@

\begin{lemma}\label{lem:expRvlamphi}
$W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma$ is a continuous function with $\gamma(0) = 0$.
\end{lemma}
\begin{IEEEproof}
In this lemma, as in Lemma~\ref{lem:k2conv}, we work under the assumption that $0 \leq \lambda < \frac{\pi}{M}$.  An analgous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  Recalling that $f(r,\phi)$ is the joint pdf of $R_1$ and $\Phi_1$, 
\begin{align}
W(\lambda) &= \expect R_1 v(\lambda, \Phi_1) \nonumber  \\
&= \int_0^{2\pi}\int_{0}^\infty r v(\lambda, \phi) f(r,\phi) dr d\phi \nonumber  \\ 
&= \int_0^{2\pi} v(\lambda, \phi) g(\phi) d\phi \nonumber \\
&= \sum_{k \in \ints} \int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi. \label{eq:Winfsum}
\end{align}
Now, for $k = 1, \dots, M-1$ we have $0 < \psi_{k-1} < \psi_k < 2\pi$, and so, using~\eqref{eq:vk},
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) &g(\phi) d\phi = \int_{\psi_{k-1}}^{\psi_{k}} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \lambda a_k(\lambda) + \lambda b_k(\lambda) + \lambda c_k(\lambda),
\end{align*}
where, for $k = 1, \dots, M-1$,
\begin{equation}\label{eq:ak}
a_k(\lambda) = \int_{\psi_k-\lambda}^{\psi_k}\eta_k(\lambda, \phi) g(\phi) d\phi,
\end{equation}
\[
b_k(\lambda) = \zeta_k(\lambda) \int_{\psi_{k-1}}^{\psi_k -\lambda}g(\phi) d\phi,
\]
\begin{equation}\label{eq:ck}
c_k(\lambda) = \frac{1}{\lambda} \int_{\psi_{k} - \lambda}^{\psi_{k}} s_k(\phi) g(\phi) d\phi.
\end{equation}
Both $a_k(\lambda)$ and $b_k(\lambda)$ converge to zero as $\lambda$ goes to zero, and, since $g$ is continuous, $c_k(\lambda)$ converges to 
\[
s_k(\psi_k)g(\psi_k) = -2\sin(\tfrac{\pi}{M}) g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M})
\]
as $\lambda$ goes to zero from above.  We are only interested in the limit from above because we are working under the assumption that that $0 \leq \lambda < \frac{\pi}{M}$.  The analgous argument when $-\tfrac{\pi}{M} \leq \lambda < 0$ would involve limits as $\lambda$ approaches zero from below.  We actually only require $g$ to be continuous at $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$ for each $k = 0, 1, \dots, M-1$, and the requirements of Theorem~\ref{thm:normality} could be weakened in this sense.  Here, the continuity of $g$ is garaunteed by the assumption that the noise $w_1$ is circularly symetric.

@@

\begin{lemma}\label{lem:empiricprocc} Let $Q_L(\lambda) = \expect R_L(\lambda) - \expect R_L(0)$ where the function $R_L$ is defined in~\eqref{eq:RLdef}.  Then,
\[
\sqrt{L}\big( R_L(\hat{\lambda}_L) - Q_L(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} R_L(0).
\]
\end{lemma}
\begin{IEEEproof}
Put 
\begin{equation}\label{eq:WLdef}
W_L(\lambda) = \sqrt{L}\big( R_L(\lambda) - Q_L(\lambda) - R_L(0) \big)
\end{equation}
so that
\[
\sqrt{L}\big( R_L(\hat{\lambda}_L) - Q_L(\hat{\lambda}_L) \big) = W_L(\hat{\lambda}_L) + \sqrt{L} R_L(0)
\]
Lemma~\ref{lem:ZYLempiricproc} in the Appendix shows that for any $\delta > 0$ and $\nu > 0$, there exists $\epsilon > 0$ such that
\[
\Pr\left\{ \sup_{\sabs{\lambda}<\epsilon}\sabs{W_L(\lambda)} > \delta  \right\} < \nu
\]
for all positive integers $L$.  Since $\hat{\lambda}_L$ converges almost surely to zero, it follows that for any $\epsilon > 0$,
\[
\lim_{L\rightarrow\infty}\prob\left\{ \sabs{\hat{\lambda}_L} \geq \epsilon \right\} = 0
\] 
and therefore $\prob\{ \sabs{\hat{\lambda}_L} \geq \epsilon \} < \nu$ for all sufficiently large $L$.  Now
\begin{align*}
  \prob&\left\{\sabs{ W_L(\hat{\lambda}_L) } > \delta \right\} \\
&= \prob\left\{ \sabs{W_L(\hat{\lambda}_L)} > \delta \;\text{and} \; \sabs{\hat{\lambda}_L} < \epsilon \right\} \\
&\hspace{0.7cm} + \prob\left\{ \sabs{W_L(\lambda_L)} > \delta  \;\text{and} \; \sabs{\hat{\lambda}_L} \geq \epsilon \right\} \\
&\leq \prob\left\{  \sup_{\lambda < \epsilon} \sabs{ W_L(\lambda) } > \delta \right\} + \prob\left\{ \sabs{\hat{\lambda}_L} \geq \epsilon \right\} \\
&\leq 2\nu.
\end{align*}
for all sufficiently large $L$.  Since $\nu$ and $\delta$ can be chosen arbitrarily small, it follows that $W_L(\hat{\lambda}_L)$ converges in probability to zero as $N\rightarrow\infty$.
\end{IEEEproof}

\begin{lemma}\label{lem:convdistGLdash}
The distribution of $\sqrt{L}R_L(0)$ converges to the normal with zero mean and variance $pA_1 + dA_2$.
\end{lemma}
\begin{IEEEproof}
Observe that 
\[
\sqrt{L} R_L(0) = \frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) + \frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\sfracpart{\Phi_i}.
\]
From the standard central limit the distribution of
\[
\frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) = \sqrt{\frac{\sabs{P}}{L}} \frac{1}{\sqrt{\sabs{P}}} \sum_{i \in P} R_i \sin(\Phi_i) 
\]
converges to the normal with mean $\sqrt{p}\expect R_1 \sin(\Phi_1) = 0$ as a result of~\eqref{eq:expectImpartRphi}, and variance
\[
p A_1 = p \expect R_1^2 \sin^2(\Phi_1).
\]
Similarly, the distribution of 
\[ 
\frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} = \sqrt{\frac{\sabs{D}}{L}} \frac{1}{\sqrt{\sabs{D}}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} 
\]
converges to the normal with mean $\sqrt{d}\expect R_1 \sin\fracpart{\Phi_1} = 0$ as a result of Lemma~? BLERG, and variance
\[
d A_2 = d \expect R_1^2 \sin^2\fracpart{\Phi_1}.
\]
\end{IEEEproof}

\begin{lemma}\label{lem:empiricprocforrho} Let $T_L(\lambda) = \expect G_L(\lambda)$.  Then
\[
\sqrt{L}\big( G_L(\hat{\lambda}_L) - T_L(\hat{\lambda}_L) \big) = o_P(1) + X_L,
\]
where $X_L = \sqrt{L} \big( G_L(0) - T_L(0) \big)$.
\end{lemma}
\begin{IEEEproof}
Let
\begin{equation}\label{eq:YLdef}
Y_L(\lambda) = \sqrt{L}\big( G_L(\hat{\lambda}_L) - T_L(\hat{\lambda}_L) \big) - X_L
\end{equation}
so that
\[
\sqrt{L}\big( G_L(\hat{\lambda}_L) - T_L(\hat{\lambda}_L) \big) = Y_L(\lambda) + X_L
\]
Lemma~\ref{lem:ZYLempiricproc} in the appendix 
\end{IEEEproof}

@@

\begin{lemma} \label{lem:chaining}
For any $\kappa > 0$ there exists $\epsilon > 0$ such that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } < \kappa,
\]
where $X(\lambda)$ is the Gaussian process defined in~\eqref{eq:ZpsiCondGaussProc}.
\end{lemma}
\begin{IEEEproof}
Without loss of generality, assume that $\epsilon < \tfrac{\pi}{M}$.  Lemma~\ref{lem:chaining2} shows that
\begin{equation}\label{eq:supZCK1} 
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } \leq K_1 \sqrt{C_\epsilon}
\end{equation}
where $K_1$ is a finite, positive constant, and
\begin{equation}\label{eq:Cepsdefn}
C_\epsilon = \frac{2}{L}\epsilon\sum_{i\in P \cup D}R_i^2 + \frac{4}{L}\sum_{i\in P \cup D}R_i^2 I_{\epsilon}(\Phi_i)
\end{equation}
where $I_\epsilon$ is the indicator function
\[
I_{\epsilon}(x) = \begin{cases}
1, & x \in \cup_{k\in\ints}[\psi_k - \epsilon, \psi_k + \epsilon] \\
0, & \text{otherwise},
\end{cases}
\] 
and $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$.  Now,
\[
\expect C_\epsilon =  2\epsilon\expect R_1^2 + 4 \expect R_i^2 I_{\epsilon}(\Phi_i).
\]
Recalling that $f(r,\phi)$ is the joint probability density function of $R_i$ and $\Phi_i$,
\begin{align*}
\expect R_i^2 I_\epsilon(\Phi_i) &= \int_0^{2\pi} \int_{0}^\infty  r^2 f(r,\phi) I_\epsilon(\phi) dr d\phi \\ 
&= \int_0^{2\pi}g_2(\phi) I_\epsilon(\phi) d\phi 
\end{align*}
where the function
\[
g_2(\phi) = \int_{0}^\infty  r^2 f(r,\phi) dr d\phi 
\]
is continuous due to Lemma~\ref{lem:gg2cont}.  From the definition of $I_\epsilon$,
\begin{align*}
\expect R_i^2 I_\epsilon(\Phi_i) &= \sum_{k=0}^{M-1}\int_{\psi_k-\epsilon}^{\psi_k-\epsilon}g_2(\phi) d\phi \\
&= 2\epsilon \sum_{k=0}^{M-1} (g_2(\psi_k) + o(1))
\end{align*}
where $o(1)$ goes to zero as $\epsilon$ goes to zero, by the mean value theorem.  Thus $\expect R_i^2 I_\epsilon(\Phi_i) \leq K_2\epsilon$ for some constant $K_2$. Since $\sqrt{\cdot}$ is a concave function on the positive real line, and since $C_{\epsilon}$ is always positive, it follows that
\[
\expect \sqrt{C_\epsilon} \leq  \sqrt{\expect  C_\epsilon} < \sqrt{\epsilon( K_2 + 2\expect R_1^2)  }
\]
by Jensen's inequality.  Applying $\expect$ to both sides of~\eqref{eq:supZCK1},
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } \leq K_1 \sqrt{\tfrac{1}{L}\expect C_\epsilon} < K_1 \sqrt{\epsilon( K_2 + 2\expect R_1^2)}.
\]
Choosing 
\[
\epsilon = \frac{\kappa^2}{ K_1^2 ( K_2 + 2\expect R_1^2)}
\] 
completes the proof.  It remains to prove Lemma~\ref{lem:chaining2}.
\end{IEEEproof}

>>>>

%opening
\title{Carrier phase and amplitude estimation for phase shift keying using pilots and data (Appendix)}
\author{Robby McKilliam, Andre Pollok, Bill Cowley, I. Vaughan L. Clarkson and Barry Quinn
\thanks{
Supported under the Australian Government’s Australian Space Research Program.
Robby McKilliam, Andre Pollok and Bill Cowley are with the Institute for Telecommunications Research, The University of South Australia, SA, 5095.
}}

@@

%set sections and equation counters based on the previous document.
\setcounter{equation}{20}
\newcounter{lasteqplusone}
\setcounter{lasteqplusone}{\value{equation}}
\addtocounter{lasteqplusone}{1}
\setcounter{section}{9}
\newcounter{lastsecplusone}
\setcounter{lastsecplusone}{\value{section}}
\addtocounter{lastsecplusone}{1}

@@

Here we compile lemmas required for the proof almost sure convergence (Theorem~\ref{thm:consistency}) and asymptotic normality (Theorem~\ref{thm:normality}) from the paper~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  This document is not self contained and it is intended that the reader start at~\cite{McKilliam_leastsqPSKpilotsdata_2012} and refer to this document when prompted in~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  The equation reference numbers in this document start at (\arabic{lasteqplusone}).  All equation numbers less than (\arabic{lasteqplusone}) refer back to~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  The section numbers in this document start at~\arabic{lastsecplusone} and all sections before~\arabic{lastsecplusone} are contain in~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  This document is separated into 3 sections.  Section~\ref{sec:proof-almost-sureappendix} contains those lemmas required for the proof of almost sure convergence (Theorem~\ref{thm:consistency}).  Section~\ref{sec:proof-asympt-normappendix} contains those lemmas required for the proof of asymptotic normality (Theorem~\ref{thm:normality}).  Section~\ref{sec:an-empirical-process} contains proofs for lemmas that arise in Section~\ref{sec:proof-asympt-normappendix}.  These involve the proof of~\emph{tightness} for certain empirical processes~\cite{Billingsley1999_convergence_of_probability_measures,Dudley_unif_central_lim_th_1999,Shorak_emp_proc_stat_2009}.

@@

It remains to show that $G_L^\prime(\hat{\lambda}_L) = 0$.  If $\sabs{G_L(\hat{\lambda}_L)} > 0$ then $\sabs{G_L(\lambda)}$ is differentiable at $\hat{\lambda}_L$ and, since $\hat{\lambda}_L$ is a maximiser of $\sabs{G_L(\lambda)}$,
\[
0 = \frac{d \sabs{G_L(\lambda)}}{d \lambda}(\hat{\lambda}_L) = \begin{cases} 
G_L^\prime(\hat{\lambda}_L), & G_L(\hat{\lambda}_L) > 0\\
-G_L^\prime(\hat{\lambda}_L), & G_L(\hat{\lambda}_L) < 0.
\end{cases}
\]
Thus, $G_L^\prime(\hat{\lambda}_L) = 0$ if $\sabs{G_L(\hat{\lambda}_L)} > 0$.  On the other hand $\sabs{G_L(\hat{\lambda}_L)} = 0$ only if $G_L(\lambda) = 0$ for all $\lambda \in \reals$, and in this case $G_L^\prime(\hat{\lambda}_L) = 0$ also. 
\end{IEEEproof}

@@

\begin{lemma}\label{lem:expRvlamphi}
$W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma$ is a continuous function with $\gamma(0) = 0$.
\end{lemma}
\begin{IEEEproof}
In this lemma, as in Lemma~\ref{lem:k2conv}, we work under the assumption that $0 \leq \lambda < \frac{\pi}{M}$.  An analgous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  Recalling that $f(r,\phi)$ is the joint pdf of $R_1$ and $\Phi_1$, 
\begin{align}
W(\lambda) &= \expect R_1 v(\lambda, \Phi_1) \nonumber  \\
&= \int_0^{2\pi}\int_{0}^\infty r v(\lambda, \phi) f(r,\phi) dr d\phi \nonumber  \\ 
&= \int_0^{2\pi} v(\lambda, \phi) g(\phi) d\phi \nonumber \\
&= \sum_{k \in \ints} \int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi. \label{eq:Winfsum}
\end{align}
Now, for $k = 1, \dots, M-1$ we have $0 < \psi_{k-1} < \psi_k < 2\pi$, and so, using~\eqref{eq:vk},
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) &g(\phi) d\phi = \int_{\psi_{k-1}}^{\psi_{k}} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \lambda a_k(\lambda) + \lambda b_k(\lambda) + \lambda c_k(\lambda),
\end{align*}
where, for $k = 1, \dots, M-1$,
\begin{equation}\label{eq:ak}
a_k(\lambda) = \int_{\psi_k-\lambda}^{\psi_k}\eta_k(\lambda, \phi) g(\phi) d\phi,
\end{equation}
\[
b_k(\lambda) = \zeta_k(\lambda) \int_{\psi_{k-1}}^{\psi_k -\lambda}g(\phi) d\phi,
\]
\begin{equation}\label{eq:ck}
c_k(\lambda) = \frac{1}{\lambda} \int_{\psi_{k} - \lambda}^{\psi_{k}} s_k(\phi) g(\phi) d\phi.
\end{equation}
Both $a_k(\lambda)$ and $b_k(\lambda)$ converge to zero as $\lambda$ goes to zero, and, since $g$ is continuous at $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$ for each $k = 0, 1, \dots, M-1$ by Proposition~\ref{prop:gg2cont} in~\cite{McKilliam_leastsqPSKpilotsdata_2012}, it follows $c_k(\lambda)$ converges to 
\[
s_k(\psi_k)g(\psi_k) = -2\sin(\tfrac{\pi}{M}) g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M})
\]
as $\lambda$ goes to zero from above.  We are only interested in the limit from above because we are working under the assumption that $0 \leq \lambda < \frac{\pi}{M}$.  The analgous argument when $-\tfrac{\pi}{M} \leq \lambda < 0$ would involve limits as $\lambda$ approaches zero from below.

@@

\begin{lemma}\label{lem:empiricprocc} Let $Q_L(\lambda) = \expect R_L(\lambda) - \expect R_L(0)$ where the function $R_L$ is defined in~\eqref{eq:RLdef}.  Then,
\[
\sqrt{L}\big( R_L(\hat{\lambda}_L) - Q_L(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} R_L(0).
\]
\end{lemma}
\begin{IEEEproof}
Put 
\begin{equation}\label{eq:WLdef}
W_L(\lambda) = \sqrt{L}\big( R_L(\lambda) - Q_L(\lambda) - R_L(0) \big)
\end{equation}
so that
\[
\sqrt{L}\big( R_L(\hat{\lambda}_L) - Q_L(\hat{\lambda}_L) \big) = W_L(\hat{\lambda}_L) + \sqrt{L} R_L(0)
\]
Lemma~\ref{lem:ZYLempiricproc} in Section~\ref{sec:an-empirical-process} shows that for any $\delta > 0$ and $\nu > 0$, there exists $\epsilon > 0$ such that
\[
\Pr\left\{ \sup_{\sabs{\lambda}<\epsilon}\sabs{W_L(\lambda)} > \delta  \right\} < \nu
\]
for all positive integers $L$.  Since $\hat{\lambda}_L$ converges almost surely to zero, it follows that for any $\epsilon > 0$,
\[
\lim_{L\rightarrow\infty}\prob\left\{ \sabs{\hat{\lambda}_L} \geq \epsilon \right\} = 0
\] 
and therefore $\prob\{ \sabs{\hat{\lambda}_L} \geq \epsilon \} < \nu$ for all sufficiently large $L$.  Now
\begin{align*}
  \prob&\left\{\sabs{ W_L(\hat{\lambda}_L) } > \delta \right\} \\
&= \prob\left\{ \sabs{W_L(\hat{\lambda}_L)} > \delta \;\text{and} \; \sabs{\hat{\lambda}_L} < \epsilon \right\} \\
&\hspace{0.7cm} + \prob\left\{ \sabs{W_L(\lambda_L)} > \delta  \;\text{and} \; \sabs{\hat{\lambda}_L} \geq \epsilon \right\} \\
&\leq \prob\left\{  \sup_{\lambda < \epsilon} \sabs{ W_L(\lambda) } > \delta \right\} + \prob\left\{ \sabs{\hat{\lambda}_L} \geq \epsilon \right\} \\
&\leq 2\nu.
\end{align*}
for all sufficiently large $L$.  Since $\nu$ and $\delta$ can be chosen arbitrarily small, it follows that $W_L(\hat{\lambda}_L)$ converges in probability to zero as $N\rightarrow\infty$.
\end{IEEEproof}

\begin{lemma}\label{lem:convdistGLdash}
The distribution of $\sqrt{L}R_L(0)$ converges to the normal with zero mean and variance $pA_1 + dA_2$.
\end{lemma}
\begin{IEEEproof}
Observe that 
\[
\sqrt{L} R_L(0) = \frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) + \frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\sfracpart{\Phi_i}.
\]
From the standard central limit the distribution of
\[
\frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) = \sqrt{\frac{\sabs{P}}{L}} \frac{1}{\sqrt{\sabs{P}}} \sum_{i \in P} R_i \sin(\Phi_i) 
\]
converges to the normal with mean $\sqrt{p}\expect R_1 \sin(\Phi_1) = 0$ as a result of~\eqref{eq:expectImpartRphi}, and variance
\[
p A_1 = p \expect R_1^2 \sin^2(\Phi_1).
\]
Similarly, the distribution of 
\[ 
\frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} = \sqrt{\frac{\sabs{D}}{L}} \frac{1}{\sqrt{\sabs{D}}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} 
\]
converges to the normal with mean $\sqrt{d}\expect R_1 \sin\fracpart{\Phi_1} = 0$ as a result of Lemma~\ref{lem:expectImRfracpart}, and variance
\[
d A_2 = d \expect R_1^2 \sin^2\fracpart{\Phi_1}.
\]
\end{IEEEproof}

\begin{lemma}\label{lem:expectImRfracpart}
$\expect R_1 \sin\fracpart{\Phi_1} = 0$.
\end{lemma}
\begin{IEEEproof}
Recalling the $f(r,\phi)$ is the joint pdf of $R_1$ and $\Phi_1$, we have
\begin{align*}
\expect R_1 \sin\fracpart{\Phi_1} &= \int_{0}^{2\pi} \int_{0}^\infty r \sin\fracpart{\phi} f(r,\phi) dr d\phi \\
&= \int_{-\pi}^{\pi} \sin\fracpart{\phi} g(\phi) d\phi,
\end{align*}
where $g$ is defined in the statement of Theorem~\ref{thm:normality} and the change in bounds from $0, 2\pi$ to $-\pi,\pi$ is valid because both $\sin\fracpart{\phi}$ and $g(\phi)$ are periodic with period $2\pi$.  Propostion~\ref{prop:gg2cont} in \cite{McKilliam_leastsqPSKpilotsdata_2012} shows that $g$ is even on $(-\pi,\pi)$.  Also $\sin\fracpart{\cdot}$ has period $\tfrac{2\pi}{M}$ and is odd on $(-\frac{\pi}{M}, \tfrac{\pi}{M})$.  So, for any $k \in \ints$ and $\phi \in (-\tfrac{\pi}{M}, 0)$,
\[
g(-\phi + k \tfrac{\pi}{M}) = g(\phi - k \tfrac{\pi}{M})
\]
and
\[
\sin\fracpart{-\phi + k \tfrac{\pi}{M}} = -\sin\fracpart{\phi - k \tfrac{\pi}{M}}.
\]
Now,
\begin{align*}
I_k &= \int_{-(k+1)\tfrac{\pi}{M}}^{-k\tfrac{\pi}{M}}\sin\fracpart{\phi} g(\phi) d\phi + \int_{k\tfrac{\pi}{M}}^{(k+1)\tfrac{\pi}{M}}\sin\fracpart{\phi} g(\phi) d\phi \\
&= \int_{-\tfrac{\pi}{M}}^{0}\sin\fracpart{\phi -  k\tfrac{\pi}{M}} g(\phi - k\tfrac{\pi}{M}) d\phi \\
&\hspace{1cm}+ \int_{0}^{\tfrac{\pi}{M}}\sin\fracpart{\phi + k\tfrac{\pi}{M}} g(\phi + k\tfrac{\pi}{M}) d\phi \\
&= 0
\end{align*}
for all integers $k$ because
\begin{align*}
\int_{0}^{\tfrac{\pi}{M}}&\sin\fracpart{\phi + k\tfrac{\pi}{M}} g(\phi + k\tfrac{\pi}{M}) d\phi \\
&= \int_{-\tfrac{\pi}{M}}^{0}\sin\fracpart{-\phi + k\tfrac{\pi}{M}} g(-\phi + k\tfrac{\pi}{M}) d\phi \\
&= -\int_{-\tfrac{\pi}{M}}^{0}\sin\fracpart{\phi - k\tfrac{\pi}{M}} g(\phi - k\tfrac{\pi}{M}) d\phi.
\end{align*}
Observe that the intervals
\[
 [-(k+1)\tfrac{\pi}{M},-k\tfrac{\pi}{M}] \cup [k\tfrac{\pi}{M},(k+1)\tfrac{\pi}{M}], \;\;\; k = 0, \dots, M-1
\]
partition $[-\pi, \pi]$, and so
\[
\expect R_1 \sin\fracpart{\Phi_1} = \int_{-\pi}^{\pi} \sin\fracpart{\phi} g(\phi) d\phi = \sum_{k=0}^{M-1} I_k = 0.
\]
\end{IEEEproof}

\begin{lemma}\label{lem:empiricprocforrho} Let $T_L(\lambda) = \expect G_L(\lambda)$.  Then
\[
\sqrt{L}\big( G_L(\hat{\lambda}_L) - T_L(\hat{\lambda}_L) \big) = o_P(1) + X_L,
\]
where $X_L = \sqrt{L} \big( G_L(0) - T_L(0) \big)$.
\end{lemma}
\begin{IEEEproof}
Let
\begin{equation}\label{eq:YLdef}
Y_L(\lambda) = \sqrt{L}\big( G_L(\hat{\lambda}_L) - T_L(\hat{\lambda}_L) \big) - X_L
\end{equation}
so that
\[
\sqrt{L}\big( G_L(\hat{\lambda}_L) - T_L(\hat{\lambda}_L) \big) = Y_L(\lambda) + X_L
\]
Lemma~\ref{lem:ZYLempiricproc} in Section~\ref{sec:an-empirical-process} shows that for any $\delta > 0$ and $\nu > 0$, there exists $\epsilon > 0$ such that
\[
\Pr\left\{ \sup_{\sabs{\lambda}<\epsilon}\sabs{Y_L(\lambda)} > \delta  \right\} < \nu.
\]
The proof now follows by an argument analogous to that in Lemma~\ref{lem:empiricprocc}.
\end{IEEEproof}

@@

\begin{lemma} \label{lem:chaining}
For any $\kappa > 0$ there exists $\epsilon > 0$ such that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } < \kappa,
\]
where $X(\lambda)$ is the Gaussian process defined in~\eqref{eq:ZpsiCondGaussProc}.
\end{lemma}
\begin{IEEEproof}
Without loss of generality, assume that $\epsilon < \tfrac{\pi}{M}$.  Lemma~\ref{lem:chaining2} shows that
\begin{equation}\label{eq:supZCK1} 
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } \leq K_1 \sqrt{C_\epsilon}
\end{equation}
where $K_1$ is a finite, positive constant, and
\begin{equation}\label{eq:Cepsdefn}
C_\epsilon = \frac{2}{L}\epsilon\sum_{i\in P \cup D}R_i^2 + \frac{4}{L}\sum_{i\in P \cup D}R_i^2 I_{\epsilon}(\Phi_i)
\end{equation}
where $I_\epsilon$ is the indicator function
\[
I_{\epsilon}(x) = \begin{cases}
1, & x \in \cup_{k\in\ints}[\psi_k - \epsilon, \psi_k + \epsilon] \\
0, & \text{otherwise},
\end{cases}
\] 
and $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$.  Now,
\[
\expect C_\epsilon =  2\epsilon\expect R_1^2 + 4 \expect R_i^2 I_{\epsilon}(\Phi_i).
\]
Recalling that $f(r,\phi)$ is the joint probability density function of $R_i$ and $\Phi_i$,
\begin{align*}
\expect R_i^2 I_\epsilon(\Phi_i) &= \int_0^{2\pi} \int_{0}^\infty  r^2 f(r,\phi) I_\epsilon(\phi) dr d\phi \\ 
&= \int_0^{2\pi}g_2(\phi) I_\epsilon(\phi) d\phi 
\end{align*}
where the function
\[
g_2(\phi) = \int_{0}^\infty  r^2 f(r,\phi) dr d\phi 
\]
is continuous at $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$ for each $k = 0, 1, \dots, M-1$ by Proposition~\ref{prop:gg2cont} in~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  From the definition of $I_\epsilon$,
\begin{align*}
\expect R_i^2 I_\epsilon(\Phi_i) &= \sum_{k=0}^{M-1}\int_{\psi_k-\epsilon}^{\psi_k-\epsilon}g_2(\phi) d\phi \\
&= 2\epsilon \sum_{k=0}^{M-1} (g_2(\psi_k) + o(1))
\end{align*}
where $o(1)$ goes to zero as $\epsilon$ goes to zero, by the mean value theorem.  Thus $\expect R_i^2 I_\epsilon(\Phi_i) \leq K_2\epsilon$ for some constant $K_2$. Since $\sqrt{\cdot}$ is a concave function on the positive real line, and since $C_{\epsilon}$ is always positive, it follows that
\[
\expect \sqrt{C_\epsilon} \leq  \sqrt{\expect  C_\epsilon} < \sqrt{\epsilon( K_2 + 2\expect R_1^2)  }
\]
by Jensen's inequality.  Applying $\expect$ to both sides of~\eqref{eq:supZCK1},
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } \leq K_1 \sqrt{\tfrac{1}{L}\expect C_\epsilon} < K_1 \sqrt{\epsilon( K_2 + 2\expect R_1^2)}.
\]
Choosing 
\[
\epsilon = \frac{\kappa^2}{ K_1^2 ( K_2 + 2\expect R_1^2)}
\] 
completes the proof.  It remains to prove Lemma~\ref{lem:chaining2}.
\end{IEEEproof}
